О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
Proofreading by Usachev - p. 8

\begin{theorem}
	For every $\varepsilon > 0$ there exists a number $n_0$ such that the inequality
	\begin{equation}
		d(2,n) \geq n\cdot(3^{1/4}\cdot2^{-3/2} - \varepsilon)
	\end{equation}
	holds for every $n>n_0$.
\end{theorem}

@@

\begin{definition}
	\cite{kurz2005characteristic}
	A squarefree number $q$ is called the \textit{characteristic} of $M\in\mathfrak{M}(2,\mathbb{N})$,
	if for any points $M_1, M_2, M_3 \in M$ the area of triangle $M_1 M_2 M_3$
	is $p_{1,2,3}\sqrt{q}$ for some rational $p_{1,2,3}$.
\end{definition}
For given $M\in\mathfrak{M}(2,\mathbb{N})$, the characteristic is determined uniquely.

Facher sets are the simplest ones of planar integral point sets.
It is shown that for $9\leq n \leq 122$ all the optimal sets are facher~\cite{kurz2008minimum}.
For every cardinality $n$ and every squarefree number $q$
there exists a facher set $M\in\mathfrak{M}(2,n)$ with characteristic $q$~\cite[Theorem 5]{our-vmmsh-2018}.
In~\cite{antonov2008maximal}, the facher sets of characteristic 1 were investigated; they were called \textit{semi-crabs}.

@@

Now we will improve the Solymosi's result.

\begin{construction}
	\label{con:planar_set_with_minimeter_1}
	Let us choose a positive integer $k > 1$ and take
	\begin{equation}
		a = 2^{2^k} - 1
		.
	\end{equation}
	Then
	\begin{equation}
		\label{eq:a_equiv_3_mod_4}
		a \equiv 3 \mod 4
	\end{equation}
	and, moreover,
	\begin{multline}
		a = \left(2^{2^{k-1}}\right)^2 - 1
		=
		\left(2^{2^{k-1}} + 1\right) \left(2^{2^{k-1}} - 1\right)
		=
		\\=
		\left(2^{2^{k-1}} + 1\right) \left(2^{2^{k-2}} + 1\right) \cdot ... \cdot \left(2^{2^1} + 1\right) \left(2^2 - 1\right)
		.
	\end{multline}
	We take $d_j = 2^{2^j} + 1$ for $1 \leq j \leq k-1$.
	Then $d_j \equiv 1 \mod 4$.

>>>>

\begin{theorem}
	For every $\varepsilon > 0$ there exists a number $n_0$ such that the inequality
	\begin{equation}
		d(2,n) \geq n\cdot(3^{1/4}\cdot 2^{-3/2} - \varepsilon)
	\end{equation}
	holds for every $n>n_0$,
	that is
	\begin{equation}
		\lim_{n\to\infty} \frac{d(2,n)}{n} \geq 3^{1/4}\cdot 2^{-3/2}
		.
	\end{equation}
\end{theorem}

@@

\begin{definition}
	\cite{kurz2005characteristic}
	A squarefree number $q$ is called the \textit{characteristic} of $M\in\mathfrak{M}(2,\mathbb{N})$,
	if for any points $M_1, M_2, M_3 \in M$ the area of triangle $M_1 M_2 M_3$
	is $p_{1,2,3}\sqrt{q}$ for some rational $p_{1,2,3}$.
\end{definition}
For a given $M\in\mathfrak{M}(2,\mathbb{N})$, the characteristic is determined uniquely.

Facher sets are the simplest planar integral point sets.
It is known that for $9\leq n \leq 122$ all the optimal sets are facher~\cite{kurz2008minimum}.
For every cardinality $n$ and every squarefree number $q$
there exists a facher set $M\in\mathfrak{M}(2,n)$ with characteristic $q$~\cite[Theorem 5]{our-vmmsh-2018}.
In~\cite{antonov2008maximal}, the facher sets of characteristic 1 were investigated; they were called \textit{semi-crabs}.

@@

Now we improve Solymosi's result.

\begin{construction}
	\label{con:planar_set_with_minimeter_1}
	Let us choose a positive integer $k > 1$ and set
	\begin{equation}
		a = 2^{2^k} - 1
		.
	\end{equation}
	Then
	\begin{equation}
		\label{eq:a_equiv_3_mod_4}
		a \equiv 3 \mod 4
	\end{equation}
	and, moreover,
	\begin{multline}
		a = \left(2^{2^{k-1}}\right)^2 - 1
		=
		\left(2^{2^{k-1}} + 1\right) \left(2^{2^{k-1}} - 1\right)
		=
		\\=
		\left(2^{2^{k-1}} + 1\right) \left(2^{2^{k-2}} + 1\right) \cdot ... \cdot \left(2^{2^1} + 1\right) \left(2^2 - 1\right)
		.
	\end{multline}
	We take $d_j = 2^{2^j} + 1$ for $1 \leq j \leq k-1$.
	Then $d_j \equiv 1 \mod 4$.
